Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-16 writeups/dissertation/dissertation.tex
foo

A plot of model accuracy for components of both the Random Permutation and Bayesian models and isolated by subset are included in Figure \ref{figContextSubsets}.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-contextStandardByGroupT-crop.pdf}}}
  \caption{Model accuracy for each of the four Twitter popular-users subsets}
  \label{figContextOffsetT}
\end{figure}

Although there is a main effect of subset, there are no practically significant interactions.
Relative model performance remains consistent across the four subsets.
This means that model behavior for the popular-users subset for Twitter can be interpreted as behavior that will persist across different time periods,
if the same method of choosing popular hashtags is done at a later date.
It may be more general that model behavior also does not depend on the specific method of choosing the popular hashtags, but since only a single method was used for this analysis, this is still an open question.

@@

>>>>

A plot of model accuracy for components of both the Random Permutation and Bayesian models and isolated by Twitter popular-users subset are included in Figure \ref{figContextSubsets}.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-contextStandardByGroupT-crop.pdf}}}
  \caption{Model accuracy for each of the four Twitter popular-users subsets}
  \label{figContextSubsets}
\end{figure}

Although there is a main effect of subset, there are minimal to no practically significant interactions.
Relative model performance remains consistent across the four subsets.

Since the interactions across popular-users datasets are minimal, model behavior for the popular-users subset for Twitter can be interpreted as behavior that will persist across different time periods,
if the same method of choosing popular hashtags is done at a later date.
It may be more general that model behavior also does not depend on the specific method of choosing the popular hashtags, but since only a single method was used for this analysis,
the results from this study cannot by themselves be used to answer this question.

@@

\textcite{Sahlgren2008} looked at several ways to handle the commonly-occurring stop words for the random-permutation model:
A data-driven frequency-weighted approach was tried, along with using a previously-derived stoplist, and no stop word removal at all.
Removing the high-frequency words in the dataset showed the highest performance increase compared to no stop word removal, and uing a previously-derived stoplist hardly increased performance.
However, \citeauthor{Sahlgren2008} did not try to weight the stop words, and only tried methods to remove them.
So alongside looking at frequency weighting, previously derived, and no stop word removal, \textcite{Stanley2013}'s method of attentuating stop words based on Entropy was also explored.

The runs from the Twitter popular-users and StackOverflow randomly-sampled datasets were used for the analysis.
Both the random permutation and Bayesian models were tested.
Activations for context were computed by using the two methods for stop word removal, the entropy weighting method, and no method (i.e., no stop word processing).

\paragraph{Determing Frequency Cutoff}

The same previously-derived stoplist from FIXME that \textcite{Sahlgren2008} used was used for this analysis,
The same entropy weighting method using by \textcite{Stanley2013} was examined,
and the same method of removing the high-frequency words from \citeauthor{Sahlgren2008} was used.

However a cutoff point must be identified and used in order to remove the high-frequency words.
\textcite{Sahlgren2008} used a cutoff where words that occurred more than \num{15000} times were removed.
Since the StackOverflow and Twitter datasets are much larger than the datasets used by \citeauthor{Sahlgren2008}, the same cutoff could not be used.
The ideal cutoff was determined by choosing the value where the standard deviation of the counts for each word for each of the tags were all relatively small.
That is, the spikes were suppressed for standard deviations for particular tags that still contained words with a very large number of observations.
The cutoff was also chosen such that the size of the spikes was about as large as the spikes generated when the entropy method was used.

The plot of the standard deviations across tags that was used to identify the cutoff for StackOverflow and Twitter is included in Figures \ref{figContextCutoffSO} and \ref{figContextCuttoffT}.

FIXME:

The no-removal plot shows the size of the spikes when high-frequency words are removed.
The entropy plot shows how the size decreases by more than an order of magnitude when the entropy weighting measure is used.
The cutoff was chosen such that the frequency plot looks similar to the entropy plot, with spikes around the same size.
Note that using a previously-defined stoplist does not remove some of the remaining high-frequency words in these datasets, which hints that this method may not be ideal when model accuracy is examined.
The cuttoff that produced the frequency plot is where a word represents more than \num{.0004} occurrences in the dataset.
This may or may not be equal to the value for \textcite{Sahlgren2008}, since that number was expressed in total observations (not as a percentage), and the total number of words in the dataset were not given.

Also, no strong claims are being made that the cutoff identified is the ideal frequency percentage cutoff for all datasets when a frequency cutoff is used.
The method used to identify this cutoff was simply aimed to find a reasonable value where comparisons between a frequency cutoff and entropy weighting techniques would be equitable.
